Query Optimization for Dynamic Imputation

### 2017-05-10 paper/experiments.tex
pareto plot with representative plans, and caption explaining precision point

\begin{figure}
\includegraphics[width=\columnwidth]{figures/pareto_frontiers_plot.png}
\caption{\ProjectName{}'s final Pareto frontier for \Cref{q1} and \Cref{q6}. The user can tradeoff between the plans by adjusting values of $\alpha$. Depending on the query
there may be small clusters of plans centered around a similar penalty or time value. The frontier is produced before executing a plan and can be exposed
to the user.}
\label{fig:pareto-frontiers}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.5]{figures/pareto_frontiers_plot.png}
\caption{\ProjectName{}'s final Pareto frontier for \Cref{q1} and \Cref{q6}. The user can tradeoff between the plans by adjusting values of $\alpha$. Depending on the query
there may be small clusters of plans centered around a similar penalty or time value. This may occur as no plan actually dominates another at a given level of precision.
For clarity, we have removed from the plot plans that provide similar tradeoffs in either dimension. }
\label{fig:pareto-frontiers}
\end{figure}
